### 2018-06-19 doc/latex/03-Simulator.tex
Add info about calibrator file
Fix commutes doc

The MapViewer component can be used to explore a generated GeoGrid.
From the workspace directory, the MapViewer can be started by using \mbox{``\texttt{./bin/mapviewer}''}. No additional command line options are available.
To open a GeoGrid use the menu option \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
The circular markers indicate a city or sub-municipality. The square markers indicate the ``parent'' city of sub-municipalities, they don't have a population.
By clicking on the square marker, all the sub-municipalities will be selected.
When one ore more cities is selected the details are shown in the right sidebar. For example a list of ContacCenters in the current selected Location. When a ContactCenter is clicked, the ContactPools of the clicked ContactCenter will be shown.
When holding the Ctrl key and clicking multiple markers all clicked markers will be selected.  Multiple cities in a rectangle can be selected by holding the control key and left mouse button while dragging. Clicking on the map will deselect all cities. Hold the Alt key while panning the map to prevent deselection.
Ctrl+ A can be used to select all cities, while Ctrl + F can be used to fit the viewport of the map so all cities are visible.
To show commutes of a city, first enable the \texttt{View -> Show Commutes} option and then select a city.
While simulating a blue marker indicates that no one is infected at that location. As soon as some people get infected the marker will become green, to eventually become red when more people are infected.
The visible area of a map can be exported to an image file using \texttt{File -> Export to image}.

@@

\begin{description}
    \item[\texttt{--config}] \ \\
        Specifies the run configuration parameters to be used for the simulation.
        If this is provided multiple times, the calibration is performed on all given simulations.
        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
    \item[\texttt{--testcases}] \ \\
        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
    \item[\texttt{--multiple}]\ \\
        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
    \item[\texttt{--single}]\ \\
        Run the simulations with the fixed seeds to determine the exact values.
    \item[\texttt{--output}]\ \\
        Write the results of the calibration to a file with given filename. This resulting file contains ...
    \item[\texttt{--write}]\ \\
        Write boxplots to files in the current directory. This creates an image for each config or testcase.
    \item[\texttt{--display}]\ \\
        Display the boxplots for the last step.
    \item[\texttt{--displayStep}]\ \\
        Display the boxplots for a specified step.
\end{description}

>>>>

The MapViewer component can be used to explore a generated GeoGrid.
From the workspace directory, the MapViewer can be started by using \mbox{``\texttt{./bin/mapviewer}''}. No additional command line options are available.
To open a GeoGrid use the menu option \texttt{File -> Open}. After loading the file, the viewport can be changed so that all markers are visible (\texttt{View -> Fit viewport}).
The circular markers indicate a city or sub-municipality. The square markers indicate the ``parent'' city of sub-municipalities, they don't have a population.
By clicking on the square marker, all the sub-municipalities will be selected.
When one ore more cities is selected the details are shown in the right sidebar. For example a list of ContacCenters in the current selected Location. When a ContactCenter is clicked, the ContactPools of the clicked ContactCenter will be shown.
When holding the Ctrl key and clicking multiple markers all clicked markers will be selected.  Multiple cities in a rectangle can be selected by holding the control key and left mouse button while dragging. Clicking on the map will deselect all cities. Hold the Alt key while panning the map to prevent deselection.
Ctrl+ A can be used to select all cities, while Ctrl + F can be used to fit the viewport of the map so all cities are visible.
To show commutes of a city, first enable the \texttt{View -> Show Commutes} option. The commutes between the selected cities will be shown.
While simulating a blue marker indicates that no one is infected at that location. As soon as some people get infected the marker will become green, to eventually become red when more people are infected.
The visible area of a map can be exported to an image file using \texttt{File -> Export to image}.

@@

\begin{description}
    \item[\texttt{--config}] \ \\
        Specifies the run configuration parameters to be used for the simulation.
        If this is provided multiple times, the calibration is performed on all given simulations.
        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
    \item[\texttt{--testcases}] \ \\
        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
    \item[\texttt{--multiple}]\ \\
        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
    \item[\texttt{--single}]\ \\
        Run the simulations with the fixed seeds to determine the exact values.
    \item[\texttt{--output}]\ \\
        Write the results of the calibration to a file with given filename.
        This resulting file contains for each configuration and each step in the simulation the mean, standard deviation, exact value using the default seed and the values found with other seeds.
        These values depend on the selected options, specifically \texttt{--multiple} and \texttt{--single}.
    \item[\texttt{--write}]\ \\
        Write boxplots to files in the current directory. This creates an image for each config or testcase.
    \item[\texttt{--display}]\ \\
        Display the boxplots for the last step.
    \item[\texttt{--displayStep}]\ \\
        Display the boxplots for a specified step.
\end{description}
